---
title: "EDRM718 Assignment#10"
Author: "Ruiqin Gao"
Data:"04/20/2020"
output: html_notebook
---

###1. Write a script to import and tidy the Johnson Elementary Project Data. 

```{r}
library(tidyverse)
ELA<-read_csv("ELA.csv", skip=3)
ELA
# Let's separate the columns
ELA1 <- ELA %>%
  separate("Tardies; Absences", into = c("Tardies", "Absences"),
           sep=";", convert = TRUE)
# Fill in the first column
#Rename the first variable name
names(ELA1)[1]<-"Room"
# Fill in the first column
ELA1 <- ELA1 %>%
  fill(Room)
#Drop missing data
ELA2 <- ELA1 %>%
  drop_na(`Student ID`) 
write_csv(ELA2, "ELA2.csv")
ELA2

```
###2.Write a script to provide summary statistics for the number of tardies and absences for each room.calcualte the statistics summary for Tardies and absences by Room
```{r}
summary.stats <- ELA2 %>%
  group_by(Room) %>%
  summarize(T_mean = mean(Tardies),
            T_sd = sd(Tardies),
            A_mean = mean(Absences),
            A_sd = sd(Absences))
summary.stats
```
###3. Write a script to show the frequency of missing data points for each quarter by room.
```{r}
freq_missing <- ELA2 %>%
  group_by(Room) %>%
  summarize(sum(is.na(`1st Quarter`)),
            sum(is.na(`2nd Quarter`)),
            sum(is.na(`3rd Quarter`)),
            sum(is.na(`4th Quarter`)))
freq_missing
```
###4Construct a graph that illustrates the median rating trends across the four quarters for the fifth-grade classes.

**The horizontal axes is poorly labeled. (-5)**

```{r}
#Let's gather data from 4 quarters as one variable
ELA3 <- ELA2 %>%
  gather(`1st Quarter`, `2nd Quarter`, `3rd Quarter`, `4th Quarter`,
         key = "Quarter",
         value = "Rating")
ELA3
median_plot <- ELA3 %>%
  group_by(Room, Quarter) %>%
  summarize(median_score = median(Rating, na.rm = TRUE)) %>%
  ggplot(aes(x = Quarter, y = median_score)) +
  geom_point (mapping=aes(x=Quarter, y=median_score))+
  labs(x="Quarter", y="Medain ELA Ratings",
       title="Medain ELA Ratings by quarter for each room")+
  facet_wrap(~ Room)
 median_plot          
```
###5 Use the NYC flights data to construct a graph that compares carriers in terms of theproportion of 2013 flights that arrived on time when traveling from New York City toAtlanta. Your graph should include a title and easy-to-read labels, including the namesof airlines rather than airline codes.


**Many carriers are missing from the graph. (-10)**


```{r}
NYC <- read_csv("NYC Flights 2013.csv")
 #Let's filter out the inforamtion we need for analysis
 NYC1 <- NYC %>%
     filter(origin == "JFK", dest == "ATL" ) %>%
     select(arr_delay, carrier, origin, dest)
NYC1
 NYC1 <- NYC1 %>%
   mutate (on_time = (arr_delay <= 0)) %>%
   drop_na(on_time)
 # Plot the graph
 plot <- NYC1 %>%
   ggplot(aes(x = carrier, fill = on_time)) +
   geom_bar(position = "fill") +
   labs(x = "Carrier", y = "Proportion",
        title = "Proportion of arriving on time by carrier")
 plot
```


